Efficient ancestry and mutation simulation with msprime 1.0

### 2021-08-12 paper.tex
Update mutation fig to join SVGs

\begin{figure}
    \includegraphics{illustrations/mutated_tree}
    \caption{
        \label{fig-mutated-trees}
        Visualisation of the separation between ancestry and mutation simulation:
        \texttt{sim\_ancestry} produces ancestry
        (\textbf{left;} shown are two trees along a 1Kb chunk of genome
        relating 200 samples),
        and \texttt{sim\_mutations} adds mutations
        (\textbf{right;} fourteen nucleotide mutations have been added).
        Graphics produced with \tskit's \texttt{draw\_svg} method.
        \plrcomment{TODO: fix up the axis labels, if we like this figure?}
        \jkcomment{Why 200 samples? Seems like far too many to me, how about 5?}
        \grgcomment{Add \texttt{sim\_ancestry} and \texttt{sim\_mutations} as subfigure titles?}
    }
\end{figure}

>>>>

\begin{figure}
    \includegraphics{illustrations/mutated_tree}
    \caption{
        \label{fig-mutated-trees}
        Visualisation of the separation between ancestry and mutation
        simulation. (A) The result of an invocation of \texttt{sim\_ancestry}
        is two trees along a 1Kb chunk of genome relating two diploid samples.
        (B) This ancestry is provided as the input to \texttt{sim\_mutations},
        which adds mutations.
        Graphics produced using \tskit's \texttt{draw\_svg} method.
    }
\end{figure}
